Plant Metagenomic Barcoding of Pollen Loads Offers Insights on the Foraging

### 2022-11-28 script/manuscript_MEE.Rmd
added an appendix image

To develop an ecologically relevant list of vascular plant species, with expected biotic pollination, which may be present at the study sites all records adjacent to the field site were downloaded from the Botanical Information and Ecology Network 'BIEN' (@bien2022), and these taxa had species distribution Dodels (SDMs) generated to predict their suitability. The predicted plant species served as a reference for which species to include in the genomic sequence databases.

@@

XX corbiculae loads had DNA extracted and underwent hyb-seq, a total of XX corbiculae samples were sequenced, XX reads were recovered from sequencing. After trimming XX seqs remained. XX reads were matched using Kraken, of the reads classified by Kraken XX reads were matched using Bracken, of the reads classified by Kraken XX reads were matched using BLAST. The number of reads per sequence varied widely (min = , $\bar{x}$, max = ), the number of loci recovered per sample ranged from (min = , max = ), and the number of reads from loci also ranged widely ().

@@

>>>>

To develop an ecologically relevant list of vascular plant species, with expected biotic pollination, which may be present at the study sites all records adjacent to the field site were downloaded from the Botanical Information and Ecology Network 'BIEN' (@bien2022), and these taxa had Species Distribution Models (SDMs) generated to predict their suitability. The predicted plant species served as a reference for which species to include in the genomic sequence databases.

@@

XX corbiculae loads had DNA extracted and underwent hyb-seq, a total of XX corbiculae samples were sequenced, XX reads were recovered from sequencing. After trimming XX seqs remained. XX reads were matched using Kraken, of the reads classified by Kraken XX reads were matched using Bracken, of the reads classified by Kraken XX reads were matched using BLAST. The number of reads per sequence varied widely (min = , $\bar{x}$, max = ), the number of loci recovered per sample ranged from (min = , max = ), and the number of reads from loci also ranged widely () **APPENDIX X**.

@@

```{r APPENDIX NUMBER LOCI WITH READS USED IN MATCHING}

knitr::include_graphics('../graphics/plots/Percent_loci_matched_by_sample.png')
